{\bf {\Large Title....}}

### 2016-07-01 ident_manu.Rnw
catident figure

The identifiability functions evaluate the ability to identify all subsets from pairwise to all parameters in the subset.  As an example, the identifiability of pairwise combinations for each of the categories are shown below.

Pairwise identifiability of the top two most sensitive parameters in each category is shown, first as a table showing all unique combinations from two to all parameters and second as a figure showing pairwise combinations.

@@

% identifiability boxplots
<<identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.  Plots in (a) show identifiability by parameter caterogires (b) shows identifiability by seleting the top 1 through 5 parameters regardless of category.  Lines represent identifiability ranges for each the number of parameters in the set.  The phytoplankton category is limited to 25 total parameters.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
# identifiability by category (all parameters with >0 L1) 
data(cat_ident)
data(top_ident)

@@

p1 <- ggplot(toplo, aes(x = N, colour = Category, group = N)) + 
  geom_point(aes(y = ave)) + 
  geom_point(aes(y = med)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0) + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank()
  ) + 
  scale_colour_brewer(palette = colset) + 
  theme(legend.position = 'none') + 
  ggtitle('(a) By parameter category')

@@

p2 <- ggplot(toplo2, aes(x = N, colour = npercat, group = N)) + 
  geom_point(aes(y = ave, shape = 'Ave')) + 
  geom_point(aes(y = med, shape = 'Med')) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0) + 
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  scale_colour_brewer(palette = colset, guide = F) + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank(), 
    legend.title = element_blank()
  ) + 
  ggtitle('(b) By top parameters, all categories')

@@

>>>>

\cref{fig:identbox} shows identifiability ranges, describe by caegory, also emphasize that selection indepedent of category may be more appropriate (better identifiability).  Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.

Note that identifiability for one phytoplankton group and one zooplankton group needs to be evaluated, lots of redundancy between groups.

@@

% identifiability boxplots
<<identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.  Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.  The phytoplankton category is limited to 25 total parameters.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
# identifiability by category (all parameters with >0 L1) 
data(cat_ident)
data(top_ident)

@@

p1 <- ggplot(toplo, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank()
  ) + 
  theme(legend.position = 'none') + 
  ggtitle('(a) By parameter category')

@@

p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank(), 
    legend.title = element_blank()
  ) + 
  ggtitle('(b) By top parameters, all categories')

@@

<<catident, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).  Parameters are selected in each category by decreasing sensitivity (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). Grey lines indicate thresholds for maximum acceptable identifiability. Selection stops after $\\gamma > 15$ or if the maximum number of parameters in a category is selected.', fig.height = 8.5, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=

# plot of sequential identifiability by category

data(tocal)
data(sens_ests_cat)

# ggplot theme
pthm <- theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 6), 
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank()
    )

# data prep, select all with coll < 15 plus one, as list
toplo <- filter(tocal$cat) %>% 
  split(., .$Category) %>% 
  lapply(function(x){

    sel <- which(x$coll < 15)
    x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .)

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 3, shape = 21, fill = 'grey') +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~Category, ncol = 1, scales = 'free') + 
  scale_x_continuous(breaks = c(1:25)) + 
  scale_y_continuous('Identifiability') +
  pthm

@

### 2016-07-01 ident_manu.tex
catident figure

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Jun 29 16:36:46 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.  Plots in (a) show identifiability by parameter caterogires (b) shows identifiability by seleting the top 1 through 5 parameters regardless of category.  Lines represent identifiability ranges for each the number of parameters in the set.  The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
\end{figure}

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Thu Jun 30 19:09:01 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.  Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.  The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
\end{figure}

\begin{figure}[!ht]

{\centering \includegraphics[width=0.6\textwidth]{figs/catident-1}

\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).  Parameters are selected in each category by decreasing sensitivity (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). Grey lines indicate thresholds for maximum acceptable identifiability. Selection stops after $\gamma > 15$ or if the maximum number of parameters in a category is selected.}\label{fig:catident}
\end{figure}
